\LARGE \bf {\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-02-26 paper.tex
Re-insert section on L2TOR project

\subsection{Application to service robots and human-robot interaction}

>>>>

\subsection{Application to human-robot interaction and spatial reasoning}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{l2tor-photo2-blind}
    \caption{A user manipulating objects on top of an RFID mat (providing object
    localisation) with a NAO robot, while an operator monitors
    the interaction on a tablet that displays an {\tt uwds view} client [photo blurred for blind review].}

    \label{fig|l2torexample}
\end{figure}

\uwds has been used within the European L2TOR project~\cite{belpaeme2015l2tor}
in order to conceptualise and visualise the spatial relations and visibility of
the physical objects that participants interact with. In one of the scenarios of this
project, participants are instructed by a NAO robot to manipulate a number of
Duplo-like animals on top of a printed background paper which serves as a
landscape (Figure~\ref{fig|l2torexample}). The robot instructions are based on
pedagogical strategies to promote spatial relation learning by object
manipulation. Such instructions include commands to place the elephant
\textit{on top} or \textit{next to} the cube, or put the giraffe \textit{inside}
the house.  To assess the performance, the robot and the operator need to
compute spatial relationships between objects from the visual perspective of the
participant.

\subsection{Application to joint-action situations}
